\vspace{-2cm} \LARGE Divergence-Free Smoothed Particle Hydrodynamics \\ \large Advanced Simulation and Visualization of Fluids in Computer Graphics

### 2016-12-14 report/paper.tex
finished writing on neighbourhood

    The cell list is implemented by using a four dimensional vector where the first three dimensions are for the x, y and z coordinates and the fourth dimension is for storing the particles belonging to the cell.
    The amount of cells are decided by dividing the scene into cells of length $H$.
    The particles are then assigned to a cell by finding the cell's coordinates that it belongs to according to Equation ~\ref{eq:assignCell}, where $vect{x}$ is the position of the particle and $vect{s}_min$ is the lowest position in the scene space.
    If the particle moves out of its cell it is reassigned to the new cell it is inside.

    \begin{equation} \label{eq:assignCell}
        \frac{\lceil{pos - s_{min}}\rceil}{H}
    \end{equation}

>>>>

    The cell list is implemented by using a four dimensional vector where the first three dimensions are for the x, y and z coordinates and the fourth dimension is for storing the particles belonging to the cell.
    The amount of cells are decided by dividing the scene into cells of length $H$.
    The particles are then assigned to a cell by finding the cell's coordinates that it belongs to according to Equation ~\ref{eq:assignCell}, where $\vect{x}$ is the position of the particle and $\vect{s}_min$ is the lowest position of the scene space.
    If the particle moves out of its cell it is reassigned to the new cell it is inside.

    \begin{equation} \label{eq:assignCell}
        \frac{\lceil{\vect{x} - \vect{s}_{min}}\rceil}{H}
    \end{equation}
